---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# msrat

msrat provides the package to evalute the software reliability from the fault data collected in the testing phase. The data used in msrat are the fault data with d-metrics and s-metrics.

The examples of d-metrics are the number of test cases, coverages, etc. for each time period such as a day and a week. They are the metrics to represent the software testing environment for the testing period, and dynamically change with the progress of software testing.

S-metrics are the number of codes, complexity, etc. and are the metrics for the software products. They are assumed to be stable through whole the software testing.

## Installation

You can install msrat from GitHub with:

```{r gh-installation, eval = FALSE}
install.packages("devtools")
devtools::install_github("SwReliab/msrat")
```

Alternatively, you can install msrat with remotes:

```{r gh-installation2, eval = FALSE}
install.packages("remotes")
remotes::install_github("SwReliab/msrat")
```

## Example

This is an example for reliability evaluation with d-metrics.

```{r example1}
### load library
library(msrat)

### load example data for d-metrics
data(dmet)

### dmet.ds1 consists of the number of days (day), the number of faults (fault), the number of testcases (tc), the cumulative number of testcases (ctc), the insrease of C0 coverage (cov) and C0 coverage (ccov).
dmet.ds1

### Esimate the model for d-metrics
(result <- fit.srm.logit(formula=fault~., data=dmet.ds1))

### Select metrics in terms of AIC
(result.aic <- step(result))

### Draw the number of faults for each day and the number of faults estimated by the model (dmvplot is in Rsrat package)
dmvfplot(fault=dmet.ds1$fault, srms=result.aic)
```

This is an example for reliability evaluation with s-metrics.

```{r example2}
### load example data for d-metrics
data(tomcat5)

### S-metrics for modules: catalina, connector, jasper, servlets, tester and webapps
#### LOC: Lines of code
#### St: The number of statements
#### Br: The number of branches
#### Co: Percentage of comments
#### Fn: The number of functions (methods)
#### Mc: Maximum complexity
#### Ac: Average complexity
tomcat5.smet

### Each module has the fault data (grouped data)
tomcat5.catalina

### List for fault data
data.tomcat5 <- list(catalina=tomcat5.catalina,
                     connector=tomcat5.connector,
                     jasper=tomcat5.jasper,
                     servlets=tomcat5.servlets,
                     tester=tomcat5.tester,
                     webapps=tomcat5.webapps)

### Estimate NHPP model (gamma model) parameters using Rsrt
# library(Rsrat)
(results.tomcat5 <- lapply(data.tomcat5,
                          function(d) fit.srm.nhpp(time=d$time,
                                                   fault=d$fault,
                                                   srm.names=c("gamma"))))

### Estimate s-metrics (LOC and St) parameters
(result <- fit.srm.poireg(formula=~LOC+St, data=tomcat5.smet, srms=results.tomcat5))

### Draw 
mvfplot(time=time, fault=fault, data=tomcat5.catalina,
        srms=list(results.tomcat5$catalina, result$srm$srms$catalina))
```
